\mytitle

### 2023-07-03 appendix.tex
Fixes to improve text for Computer Journal submission

\begin{quote}
At the time of cloning and checking all repositories in \clonewhen, paper \csname cite-PostoperativeOutcomes.RiskNet\endcsname\ still had nothing in its repository except a single file still saying ``...code coming soon...,'' despite \the\pubdelayinmonths\ months having already elapsed since the submitted paper had claimed the code could be accessed in its repository.\end{quote}

@@

Unfortunately, although using generated variables and analyses from a paper's data is a very simple technique to help make published papers more reliable, some journals and preprint servers (such as \emph{IEEE Transactions on Software Engineering}, \emph{PLOS ONE}, and \emph{arXiv\/}) do not permit papers to be submitted using \LaTeX\ source code that uses the standard \texttt{\textbackslash input}, \texttt{\textbackslash bibliography}, and other related commands. Typically they also do not support running any data collection or analysis either (which the present paper does when it clones repositories). These policies undermine the drive towards RAP and \RAPstarp.

Another program (\texttt{programs/expand.js}) was therefore written to recursively expand included files so the expanded version can be submitted adhering to any such restrictive policy. Of course, the expanded version now contains all variables as fixed constants, so the submitted paper is misleading and useless to other researchers if the data is modified --- the effort to ensure all published numbers are automatically correct is defeated. Such restrictive publishing policies undermine reproducibility.

@@

>>>>

\begin{quote}
At the time of cloning and checking all repositories in \clonewhen, paper \csname cite-PostoperativeOutcomes.RiskNet\endcsname\ still had nothing in its repository except a single file still saying ``\texttt{\ldots~code coming soon~\ldots}'' despite \the\pubdelayinmonths\ months having already elapsed since the submitted paper had claimed the code could be accessed in its repository.\end{quote}

@@

Unfortunately, although using generated variables and analyses from a paper's data is a very simple technique to help make published papers more reliable, some journals and preprint servers (such as \emph{IEEE Transactions on Software Engineering}, \emph{PLOS ONE}, \emph{arXiv}, and even the \emph{Computer Journal}, which published this paper) do not permit papers to be submitted using \LaTeX\ source code that uses the standard \texttt{\textbackslash input}, \texttt{\textbackslash bibliography}, and other related commands. Typically they also do not support running any data collection or analysis either (which the present paper does when it clones repositories). These policies undermine the drive towards RAP and \RAPstarp.

Another program (\texttt{programs/expand.js}) was therefore written to recursively expand included \LaTeX\ files so the expanded version can be submitted to any journal adhering to any such restrictive policies. It also renames and flattens the file hierarchy (e.g., copying images to be in the same directory as the expanded main \LaTeX\ file), as the journal web site did not cope with standard \LaTeX\ file naming conventions. A consequence is that the published version now contains all generated text and variables as fixed constants, so the published paper is misleading and useless to other researchers if any data is modified --- the effort to ensure all published data are automatically correct is defeated. Such technically limiting publishing policies undermine reproducibility. Fortunately, in the present case the original data and documents are still available on the Github site.

Clearly, there is still a long way to go. Such problems will put authors off using computational papers and \RAPstar\ methodologies.

@@

\section{Errata and updates to the paper}

\emph{No material added yet.}

### 2023-07-03 expanded/EXappendix.tex
Fixes to improve text for Computer Journal submission

@@

\@writefile{lot}{\contentsline {table}{\numberline {4}{\ignorespaces A simplified schematic of the publication pipeline. For clarity, the pipeline has been linearized; in general, there will be repetitive cyclic iteration and refinement. The RAP and RAP{\tt  +}\ approaches encode the normally manual steps in the pipeline workflow so that they can be run automatically, and hence reproduce the results that underpin the final paper. The encoded RAP{\tt  +}\ algorithms can be shared with other scientists, scrutinized, simplified and optimized, and themselves turned into publishable objects --- they are scientific instruments, just like thermometers or DNA sequencers. Additional schematics are provided in section \ref {supplement-RAP-diagrams} in the Supplemental Material.}}{8}{table.4}\protected@file@percent }
\newlabel{fig-pipeline}{{4}{8}{A simplified schematic of the publication pipeline. For clarity, the pipeline has been linearized; in general, there will be repetitive cyclic iteration and refinement. The RAP and \RAPstar \ approaches encode the normally manual steps in the pipeline workflow so that they can be run automatically, and hence reproduce the results that underpin the final paper. The encoded \RAPstar \ algorithms can be shared with other scientists, scrutinized, simplified and optimized, and themselves turned into publishable objects --- they are scientific instruments, just like thermometers or DNA sequencers. Additional schematics are provided in section \ref {supplement-RAP-diagrams} in the \supplement }{table.4}{}}
\@writefile{lot}{\contentsline {table}{\numberline {5}{\ignorespaces A minimum standard of RAP, based on the UK Statistics Authority summary \cite  {RAPstandard}.}}{8}{table.5}\protected@file@percent }
\newlabel{figure-RAP-summary}{{5}{8}{A minimum standard of RAP, based on the UK Statistics Authority summary \cite {RAPstandard}}{table.5}{}}

@@

@@

\@writefile{toc}{\contentsline {subsubsection}{\numberline {2.c.1}Potential code}{9}{subsubsection.2.3.1}\protected@file@percent }

@@

\@writefile{toc}{\contentsline {subsection}{\numberline {4.d}Bugs, code and programming}{15}{subsection.4.4}\protected@file@percent }
\newlabel{knowledge}{{4.d}{15}{Bugs, code and programming}{subsection.4.4}{}}

@@

@@

\@writefile{toc}{\contentsline {subsection}{\numberline {6.e}Methodological statements}{25}{subsection.6.5}\protected@file@percent }

@@

@@

\@writefile{toc}{\contentsline {subsection}{\numberline {6.f}Training to reduce technical debt}{26}{subsection.6.6}\protected@file@percent }
\newlabel{technical-debt}{{6.f}{26}{Training to reduce technical debt}{subsection.6.6}{}}

@@

@@

>>>>

\@writefile{toc}{\contentsline {section}{\numberline {15}Errata and updates to the paper}{69}{section.15}\protected@file@percent }

@@

@@

\@writefile{toc}{\contentsline {subsubsection}{\numberline {2.c.1}Potential code}{8}{subsubsection.2.3.1}\protected@file@percent }

@@

\@writefile{lot}{\contentsline {table}{\numberline {4}{\ignorespaces A simplified schematic of the publication pipeline. For clarity, the pipeline has been linearized; in general, there will be repetitive cyclic iteration and refinement. The RAP and RAP{\tt  +}\ approaches encode the normally manual steps in the pipeline workflow so that they can be run automatically, and hence reproduce the results that underpin the final paper. The encoded RAP{\tt  +}\ algorithms can be shared with other scientists, scrutinized, simplified and optimized, and themselves turned into publishable objects --- they are scientific instruments, just like thermometers or DNA sequencers. Additional schematics are provided in section \ref {supplement-RAP-diagrams} in the Supplemental Material.}}{9}{table.4}\protected@file@percent }
\newlabel{fig-pipeline}{{4}{9}{A simplified schematic of the publication pipeline. For clarity, the pipeline has been linearized; in general, there will be repetitive cyclic iteration and refinement. The RAP and \RAPstar \ approaches encode the normally manual steps in the pipeline workflow so that they can be run automatically, and hence reproduce the results that underpin the final paper. The encoded \RAPstar \ algorithms can be shared with other scientists, scrutinized, simplified and optimized, and themselves turned into publishable objects --- they are scientific instruments, just like thermometers or DNA sequencers. Additional schematics are provided in section \ref {supplement-RAP-diagrams} in the \supplement }{table.4}{}}
\@writefile{lot}{\contentsline {table}{\numberline {5}{\ignorespaces A minimum standard of RAP, based on the UK Statistics Authority summary \cite  {RAPstandard}.}}{9}{table.5}\protected@file@percent }
\newlabel{figure-RAP-summary}{{5}{9}{A minimum standard of RAP, based on the UK Statistics Authority summary \cite {RAPstandard}}{table.5}{}}

@@

@@

\@writefile{toc}{\contentsline {subsection}{\numberline {4.d}Bugs, code and programming}{16}{subsection.4.4}\protected@file@percent }
\newlabel{knowledge}{{4.d}{16}{Bugs, code and programming}{subsection.4.4}{}}

@@

@@

\@writefile{toc}{\contentsline {subsection}{\numberline {6.e}Methodological statements}{26}{subsection.6.5}\protected@file@percent }

@@

@@

\@writefile{toc}{\contentsline {subsection}{\numberline {6.f}Training to reduce technical debt}{27}{subsection.6.6}\protected@file@percent }
\newlabel{technical-debt}{{6.f}{27}{Training to reduce technical debt}{subsection.6.6}{}}

@@

\contentsline {section}{\numberline {15}Errata and updates to the paper}{69}{section.15}%

### 2023-07-03 expanded/EXpaper.tex
Fixes to improve text for Computer Journal submission

\title{\mytitle} 
\author{Harold Thimbleby}
\shortauthors{Harold Thimbleby}
\affiliation{See Change Fellow in Digital Health, Swansea University}
\email{harold@thimbleby.net}

@@

\received{30 April 2022}
\revised{8 June 2022, 3 January 2023, 31 January 2023, 12~May~2023 \& 7~June~2023} 
\accepted{30 May 2023}
\volumenumber{00} \issuenumber{0} \volumeyear{2023}

@@

\begin{table}
\vskip 1.2ex % align top of columns!
% expand table of contents paper.toc
\makeatletter
  \section*{\contentsname
    \@mkboth{\MakeUppercase\contentsname}{\MakeUppercase\contentsname}}
\makeatother\contentsline {section}{\numberline {1}Introduction}{1}{section.1}%
\contentsline {section}{\numberline {2}Background}{2}{section.2}%
\contentsline {subsection}{\numberline {2.a}Code quality concerns}{4}{subsection.2.1}%
\contentsline {subsection}{\numberline {2.b}Computable papers}{5}{subsection.2.2}%
\contentsline {subsection}{\numberline {2.c}RAP: Reproducible Analytical Pipelines}{7}{subsection.2.3}%
\contentsline {subsubsection}{\numberline {2.c.1}Potential code}{9}{subsubsection.2.3.1}%
\contentsline {subsubsection}{\numberline {2.c.2}RAP as research}{9}{subsubsection.2.3.2}%
\contentsline {section}{\numberline {3}The statistics/code analogy}{10}{section.3}%
\contentsline {subsection}{\numberline {3.a}The siren call of over-fitting code}{11}{subsection.3.1}%
\contentsline {section}{\numberline {4}The conventional role of code}{13}{section.4}%
\contentsline {subsection}{\numberline {4.a}The deceptive simplicity of code}{14}{subsection.4.1}%
\contentsline {subsection}{\numberline {4.b}The low status of coding}{15}{subsection.4.2}%
\contentsline {subsection}{\numberline {4.c}The critical role of code is often ignored}{15}{subsection.4.3}%
\contentsline {subsection}{\numberline {4.d}Bugs, code and programming}{15}{subsection.4.4}%
\contentsline {subsection}{\numberline {4.e}Long-term problems of unreliable code}{16}{subsection.4.5}%
\contentsline {section}{\numberline {5}State of the art}{17}{section.5}%
\contentsline {subsection}{\numberline {5.a}Case study: Pandemic modeling}{17}{subsection.5.1}%
\contentsline {subsection}{\numberline {5.b}Concerns with reproducibility}{18}{subsection.5.2}%
\contentsline {subsection}{\numberline {5.c}Beyond pandemic modeling}{20}{subsection.5.3}%
\contentsline {subsection}{\numberline {5.d}The lop-sided emphasis on data}{21}{subsection.5.4}%
\contentsline {section}{\numberline {6}Rethinking science that uses code}{22}{section.6}%
\contentsline {subsection}{\numberline {6.a}Software Engineering Boards}{22}{subsection.6.1}%
\contentsline {subsection}{\numberline {6.b}Extending RAP to RAP{\tt +}}{23}{subsection.6.2}%
\contentsline {subsection}{\numberline {6.c}The paper as a scientific laboratory}{24}{subsection.6.3}%
\contentsline {subsection}{\numberline {6.d}Action must be interdisciplinary}{25}{subsection.6.4}%
\contentsline {subsection}{\numberline {6.e}Methodological statements}{25}{subsection.6.5}%
\contentsline {subsection}{\numberline {6.f}Training to reduce technical debt}{26}{subsection.6.6}%
\contentsline {subsection}{\numberline {6.g}Benefits beyond science}{27}{subsection.6.7}%
\contentsline {subsection}{\numberline {6.h}Approaches to further work}{28}{subsection.6.8}%
\contentsline {section}{\numberline {7}Conclusions}{29}{section.7}%

@@

Finally, there is still a long way to go. The \emph{Computer Journal}, which should be a leading journal for publishing computational science (and which has published this paper) uses poorly documented automated and buggy paper processing software, whose obscure bugs took several weeks of hard work to overcome in order to submit the present paper. Such problems will put authors off using computational papers and \RAPstar\ methodologies.

@@

\section*{Supporting information}
\newcount\csrefcount \csrefcount=0
\def\csref{\global\advance\csrefcount by 1}
\long\def\ethics#1{\paragraph*{Ethics}#1}
\long\def\ack#1{\paragraph*{Acknowledgments}#1}

>>>>

\title{\mytitle} 
\author{Harold Thimbleby}
\shortauthors{Harold Thimbleby}
\affiliation{See Change Fellow in Digital Health, Swansea University}
\email{h.w.thimbleby@swansea.ac.uk}

@@

\received{30 April 2022}
\revised{8 June 2022, 3 January 2023, 31 January 2023, 12~May~2023 \& 7~June~2023} 
\accepted{30 May 2023}
\paperdoi{10.1093/comjnl/bxad067}
\volumenumber{00} \issuenumber{0} \volumeyear{2023}

@@

\begin{table}
\vskip 1.2ex % align top of columns!
% expand table of contents paper.toc
\makeatletter
  \section*{\contentsname
    \@mkboth{\MakeUppercase\contentsname}{\MakeUppercase\contentsname}}
\makeatother\contentsline {section}{\numberline {1}Introduction}{1}{section.1}%
\contentsline {section}{\numberline {2}Background}{2}{section.2}%
\contentsline {subsection}{\numberline {2.a}Code quality concerns}{4}{subsection.2.1}%
\contentsline {subsection}{\numberline {2.b}Computable papers}{5}{subsection.2.2}%
\contentsline {subsection}{\numberline {2.c}RAP: Reproducible Analytical Pipelines}{7}{subsection.2.3}%
\contentsline {subsubsection}{\numberline {2.c.1}Potential code}{8}{subsubsection.2.3.1}%
\contentsline {subsubsection}{\numberline {2.c.2}RAP as research}{9}{subsubsection.2.3.2}%
\contentsline {section}{\numberline {3}The statistics/code analogy}{10}{section.3}%
\contentsline {subsection}{\numberline {3.a}The siren call of over-fitting code}{11}{subsection.3.1}%
\contentsline {section}{\numberline {4}The conventional role of code}{13}{section.4}%
\contentsline {subsection}{\numberline {4.a}The deceptive simplicity of code}{14}{subsection.4.1}%
\contentsline {subsection}{\numberline {4.b}The low status of coding}{15}{subsection.4.2}%
\contentsline {subsection}{\numberline {4.c}The critical role of code is often ignored}{15}{subsection.4.3}%
\contentsline {subsection}{\numberline {4.d}Bugs, code and programming}{16}{subsection.4.4}%
\contentsline {subsection}{\numberline {4.e}Long-term problems of unreliable code}{16}{subsection.4.5}%
\contentsline {section}{\numberline {5}State of the art}{17}{section.5}%
\contentsline {subsection}{\numberline {5.a}Case study: Pandemic modeling}{17}{subsection.5.1}%
\contentsline {subsection}{\numberline {5.b}Concerns with reproducibility}{18}{subsection.5.2}%
\contentsline {subsection}{\numberline {5.c}Beyond pandemic modeling}{20}{subsection.5.3}%
\contentsline {subsection}{\numberline {5.d}The lop-sided emphasis on data}{21}{subsection.5.4}%
\contentsline {section}{\numberline {6}Rethinking science that uses code}{22}{section.6}%
\contentsline {subsection}{\numberline {6.a}Software Engineering Boards}{22}{subsection.6.1}%
\contentsline {subsection}{\numberline {6.b}Extending RAP to RAP{\tt +}}{23}{subsection.6.2}%
\contentsline {subsection}{\numberline {6.c}The paper as a scientific laboratory}{24}{subsection.6.3}%
\contentsline {subsection}{\numberline {6.d}Action must be interdisciplinary}{25}{subsection.6.4}%
\contentsline {subsection}{\numberline {6.e}Methodological statements}{26}{subsection.6.5}%
\contentsline {subsection}{\numberline {6.f}Training to reduce technical debt}{27}{subsection.6.6}%
\contentsline {subsection}{\numberline {6.g}Benefits beyond science}{27}{subsection.6.7}%
\contentsline {subsection}{\numberline {6.h}Approaches to further work}{28}{subsection.6.8}%
\contentsline {section}{\numberline {7}Conclusions}{29}{section.7}%

@@

@@

\section*{Supporting information}

%NEW
Updates and errata are included in the \supplement, which is kept up to date at \url{github.com/haroldthimbleby/improving-science}

\newcount\csrefcount \csrefcount=0
\def\csref{\global\advance\csrefcount by 1}
\long\def\ethics#1{\paragraph*{Ethics}#1}
\long\def\ack#1{\paragraph*{Acknowledgments}#1}
